Bandit Multiclass Classification

### 2018-07-18 main.tex
Add something

We can prove this equivalence considering two directions: \\
(1) If there is a solution with the class labels following a permutation, then that permutation cannot be a subsequence of the given sequence. \\
(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.

>>>>

We can prove this equivalence considering two directions: \\
(1) If there is a solution with the class labels following a permutation, then that permutation cannot be a subsequence of the given sequence. \\
(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.\\ 
They should be straightforward by trying some examples.
